A Partitioning Algorithm for Maximum Common Subgraph Problems

### 2017-02-17 paper/paper.tex
Added conauto citation
More consistent naming of the problem we're solving

\paragraph{Maximum Common \emph{Connected} Subgraph} ?? In applications,
something. The common subgraph must be connected. We consider only undirected
graphs.  Modify \McSplit\ by permitting branching only on a vertex $v$ that has
at least one non-zero element in its bit-string label.  We can represent this
information compactly, and without increasing time complexity at each search
node, by storing an extra bit with each label class.  This bit takes the value
$1$ if and only if the vertices in the class are adjacent to at least one
vertex in $M$. ?? Link to branching scheme papers.

@@

In the CP-FC algorithm, each vertex $v \in \V(\graphG)$ is represented by a
variable, whose domain corresponds to the set of vertices in $\V(\graphH)$ to which
$v$ may currently be mapped, with an additional special $\bot$ value
representing an unmapped vertex.
Given a label class $\langle \setG,\setH \rangle$ in \McSplit\, the vertices in $\setG$
correspond to variables in CP-FC. The label-class representation of domains is
possible because throughout the CP-FC algorithm for max common subgraph, the
domains of any two variables are either identical or disjoint (excluding
$\bot$, which is slightly more complicated). To the best of our knowledge, this
observation has not been made previously, and it is not exploited in other
implementations.

>>>>

\paragraph{Maximum common \emph{connected} subgraph} ?? In applications,
something. The common subgraph must be connected. We consider only undirected
graphs.  Modify \McSplit\ by permitting branching only on a vertex $v$ that has
at least one non-zero element in its bit-string label.  We can represent this
information compactly, and without increasing time complexity at each search
node, by storing an extra bit with each label class.  This bit takes the value
$1$ if and only if the vertices in the class are adjacent to at least one
vertex in $M$. ?? Link to branching scheme papers.

@@

In the CP-FC algorithm, each vertex $v \in \V(\graphG)$ is represented by a
variable, whose domain corresponds to the set of vertices in $\V(\graphH)$ to which
$v$ may currently be mapped, with an additional special $\bot$ value
representing an unmapped vertex.
Given a label class $\langle \setG,\setH \rangle$ in \McSplit\, the vertices in $\setG$
correspond to variables in CP-FC. The label-class representation of domains is
possible because throughout the CP-FC algorithm for maximum common subgraph, the
domains of any two variables are either identical or disjoint (excluding
$\bot$, which is slightly more complicated). To the best of our knowledge, this
observation has not been made previously, and it is not exploited in other
implementations.
